\bf Hierarchical Network Structure Promotes Dynamical Robustness

### 2015-07-22 tex/overview.tex
add introductory sentence to stability decomposition subsection

\subsection{Decomposition of stability over SCCs}
Let the index $i$ range over the non-zero entries $a_i$ of $A$. The entries of the Jacobian are sampled independently from a generic probability distribution $\rho_i$ for each entry. Under this assumption then
\begin{equation}\label{eq:singleresamplemutau}
\begin{aligned}
\mu(A) &= \prod_i \rho_i(a_i),\\
\tau^{(1)}(A' \mid A) &= \frac{1}{d} \sum_i \tau^{(1)}_i (A' \mid A),
\end{aligned}
\end{equation}
where
$$
\tau^{(1)}_i(A' \mid A) = \rho_i(a'_i) \prod_{j \neq i} \delta(a'_j - a_j).
$$

>>>>

\subsection{Decomposition of stability over SCCs}
We begin by expressing the stability of a network in terms of the stabilities of its SCCs. Let the index $i$ range over the non-zero entries $a_i$ of $A$. The entries of the Jacobian are sampled independently from a generic probability distribution $\rho_i$ for each entry. Under this assumption then
\begin{equation}\label{eq:singleresamplemutau}
\begin{aligned}
\mu(A) &= \prod_i \rho_i(a_i),\\
\tau^{(1)}(A' \mid A) &= \frac{1}{d} \sum_i \tau^{(1)}_i (A' \mid A),
\end{aligned}
\end{equation}
where
$$
\tau^{(1)}_i(A' \mid A) = \rho_i(a'_i) \prod_{j \neq i} \delta(a'_j - a_j).
$$
